Vagueness, Noise, and Signaling

### 2015-01-18 paper/version_02/paper.tex
Added motivation for the fixed maximum number of iterations.

We ran 50 trials of the \rdd, starting with randomly sampled sender
and receiver strategies, for each triplet of independent parameter
values: $\ns = \card{T} \in \set{6, 10, 50, 90}$, $\impairment \in
\set{0, 0.05, 0.1, 0.2, 0.3}$, $\toler \in \set{0.05, 0.1, 0.2,
  0.3}$. Each trial ran for a maximum of 200 update steps of the
\rdd. A trial was considered converged and stopped before the maximum
of 200 rounds if the total amount of change between strategies before
and after the current \rdd step was smaller than a suitably chosen
threshold. It is not guaranteed that strategies at halting time had
converged to the eventual attracting state, whether they ran for 200
rounds or not. Our notion of convergence therefore is only a
categorical measure for the speed of approaching some state in which
the force of evolutionary optimization has fallen under a
(well-considered, but eventually arbitrary) threshold. In other words,
we need to think of convergence in our sense as speed of evolution
towards the first evolutionary slowdown.\todo{check and improve
  this}

>>>>

We ran 50 trials of the \rdd, starting with randomly sampled sender
and receiver strategies, for each triplet of independent parameter
values: $\ns = \card{T} \in \set{6, 10, 50, 90}$, $\impairment \in
\set{0, 0.05, 0.1, 0.2, 0.3}$, $\toler \in \set{0.05, 0.1, 0.2,
  0.3}$. Each trial ran for a maximum of 200 update steps of the
\rdd. A trial was considered converged, and thus stopped before the maximum
of 200 rounds, if the total amount of change between strategies before
and after an \rdd step was smaller than a suitably chosen
threshold. It is not guaranteed that strategies at halting time had
converged to the eventual attracting state, whether they ran for 200
rounds or not. Our notion of convergence is therefore only a
categorical measure for reaching a certain (well-considered, but
eventually arbitrary) degree of stability. In principle, rather than
setting a hard limit on the maximum number of rounds and analyzing
convergence categorically, one could also run each trial until reaching
our criterion for convergence and analyze the number of rounds it took to get there.
Our choice was initially motivated by pragmatic concerns regarding length of
simulation time, but it is also justifiable if we reflect on the
nature of language evolution as a continuous process.
Language adapts to an ever-changing reality; it is rare, if not impossible,
that a lexicon has an infinite amount of time to neatly converge to a stable
state. Therefore, investigating speed of convergence within a limited
time frame can be seen as better reflecting the natural constraints of
language evolution.
